### 2013-05-16 context-dependence.tex
.

@@

>>>>

%%%%
\subsection{Summary statistics}

@@

The covariance calculations show that
if $p_{\ell,m}(x,y)$ is small enough (i.e.\ the pattern is not common),
then $N(x,y)$ is close to Poisson.

Using this observation, we can estimate parameters by composite likelihood,
using all $N(x,y)$ as data.

To get confidence intervals, we need to either simulate, or do something different.
If we use only a subset of patterns $\{(x_k,y_k)\}$ chosen so that $\E[M_1(x,y) M_{k+1}(x,y)]$ is small (or zero),
the entire collection $\{N(x_k,y_k)\}$ will be close to independent Poisson.
(using Stein's method)
Then we'll have the correct likelihood function for (this subset of) data, and can go Bayesian.
